Discover governing reactions from concentration data

### 2017-11-01 docs/manuscript.tex
wip

\usepackage[left=2.5cm,right=2.6cm,top=3cm,bottom=3cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[intlimits]{amsmath}
\usepackage{amssymb}
\usepackage{color}

@@

	\subsection{Regression with regularization}
	In this example we have four species $A$, $B$, $C$, and $D$ with reactions $A\xrightarrow{k_1}D$, $D\xrightarrow{k_2}A$, $D\xrightarrow{k_3}B$, $A+B\xrightarrow{k_4}C$, and $C+D\xrightarrow{k_5}B$, where $k_1=k_2=2\cdot 10^{-2}$, $k_3 = 1\cdot 10^{-2}$, and $k_4=k_5=1\cdot 10^{-4}$.

>>>>

\usepackage[left=2.5cm,right=2.6cm,top=3cm,bottom=3cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[intlimits]{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{subcaption}

@@

	\subsection{Regression with regularization}
	\label{sec:ex2}
	In this example there are four species $A$, $B$, $C$, and $D$ with reactions $A\xrightarrow{k_1}D$, $D\xrightarrow{k_2}A$, $D\xrightarrow{k_3}B$, $A+B\xrightarrow{k_4}C$, and $C+D\xrightarrow{k_5}B$, where $k_1=k_2=2\cdot 10^{-2}$, $k_3 = 1\cdot 10^{-2}$, and $k_4=k_5=1\cdot 10^{-4}$. These reactions are inserted into the ansatz library $\Theta (\cdot)$. Additionally the reactions $A\leftrightarrow B$, $A\leftrightarrow C$, and $A+C\leftrightarrow D$ are inserted into the library.

	\begin{figure}
		\centering
		\begin{subfigure}[b]{.45\textwidth}
			\includegraphics[width=\textwidth]{./figures_tex/cv_concentrations_train}
			\caption{Train data set.}
		\end{subfigure}
		~
		\begin{subfigure}[b]{.45\textwidth}
			\includegraphics[width=\textwidth]{./figures_tex/cv_concentrations_test}
			\caption{Test data set.}
		\end{subfigure}
		\caption{Train and test data sets for the example given in Section \ref{sec:ex2}.}
		\label{ex2:test-train-concentration-curves}
	\end{figure}

	The problem now is to find a suitable $\alpha$ such that a parsimonious solution is picked. To this end, cross-validation is applied. The trajectories that were used as training and test data set are depicted in Figure \ref{ex2:test-train-concentration-curves}.
